|

### 2020-06-02 paper/Manuscript.Rmd
Figures in text

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
mask              : no

@@

```{r workflow, fig.cap="Schematic illustration of the WORCS procedure"}
knitr::include_graphics("workflow_graph/workflow.png")
```

>>>>

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
mask              : no

@@

```{r workflow, fig.cap="Schematic illustration of the WORCS procedure", out.width="100%"}
knitr::include_graphics("workflow_graph/workflow.png")
```
